\section{Conclusion:}

Today there is an upsurge in the number of electronic gadgets being used. Our world is practically surrounded by number of electronic devices each day and every one of these devices has a printed circuit board at its heart. So what exactly is this printed circuit board or PCB? It is nothing but a thick non conductive substrate sheet with copper tracks carved on it instead of wires. These tracks join at different points and nodes. This PCB is used to connect various electronic parts through the designed pathways and to provide physical support to the components. PCBs can be through-hole in which tiny holes are drilled on the nodes. The holes are used to fix the electrical component in position and are then joined on the opposite side and the copper tracks link them together forming a circuit. The board and the circuit are jointly called PCB assembly. This is an old technology and is used for low-priced circuitry applications and for supporting large components like transformers and high rating capacitors. Another type of PCB is on board SMD PCB or surface mounted device PCB. Instead of holes it has tiny conducting beds where the small SMD components are placed and soldered using special equipment. These boards have higher strength and both sides can be used for components. \hfill \break

Printed circuit boards have become an integral part of all kinds of electronic components. These devices have blended so well with our lives that we do not even comprehend how important they are, not only for our expediency but for our survival. PCBs can be used for absolutely everything. There's virtually no electronic device that cannot be built using PCBs. Whether it is battery operated toys, cell phones, music players, TVs or automated aircraft. PCBs are there in most of the electronics that we use in our everyday. Other uses of PCBs include military, medical and industrial components. The use of PCBs offers many benefits; first being its smaller size in comparison to other types of circuits. Moreover a printed circuit greatly reduces the need of wires.This in turn improves the appearance of final circuit and increases its durability. It's the cheapest method for mass producers ordering in large production as it offers huge cost benefits. \hfill \break

Some of their benefits are: \hfill \break 

\begin{itemize}
\item PCBs are cost efficient and highly reliable.
\item They are economical specialize for high volume production. 
\item Easy to install, some of they have color codes for different connections.
\end{itemize} \hfill \break

The design of printed circuit boards is very specific and of high quality. This is the reason why designing of these boards is a job of an expert and requires a lot of research and development to ensure that there are no flaws in it.

\pagebreak