\section{Questionnaire:}

\begin{itemize} 
\item {\bfseries What does the LSB and the MSB?} \hfill \break

The MSB refers to the {\itshape most-significant bit} and the LSB refers to the {\itshape least-significant bit}. \hfill \break

\item {\bfseries What are the most suitable circuits to place the reference voltage at the ADC?} \hfill \break

Any type of indicator that is needed in a circuit practical applications aeither temperature sensors, signaling devices, photo-resistors, or any device that delivers a value differing as they will modify their input values. \hfill \break

\item {\bfseries Name 5 different techniques of analog to digital conversion:} \hfill \break

\begin{enumerate}
\item ADCs.
\item Basic-steps converter.
\item Staircase ramp.
\item Successive approximations.
\item Dual-slop converter.
\end{enumerate} \hfill

\item {\bfseries What is the difference between ADC0801 and ADC0804?} \hfill \break

The {\bfseries ADC0804} use successive approximations and the {\bfseries ADC0801} use {\itshape staircase ramp} technique. \hfill \break

\item {\bfseries Which of the two ADC used in practice is the fastest and why?} \hfill \break

The fastest is the successive approximations because use a {\itshape Johnson's Counter}, this allows to the ADC to find the binary-combination in the same times that output bits that the ADC has, for example if the ADC has 8 bits, then the counter will find the value in 8 cycles, others ADC like the {\itshape staircase ramp} find the most higher value in $2^{n}$ iterations.
\end{itemize}

\pagebreak